Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-22 _05_calibration_data.Rmd
re add res time

In this dataset, residence positions are marked in the `tID` column as beginning with `WP`. These can be extracted and converted into residence patches.

@@

@@

@@

# on known residence points
patch_res_known <- atl_res_patch(data_for_patch, 
                                buffer_radius = 5,
                                lim_spat_indep = 50,
                                lim_time_indep = 5,
                                min_fixes = 3)
```

>>>>

### Calculate residence time

```{r}
# load recurse
library(recurse)
```

@@

# get recurse data for a 10m radius
recurse_stats <- getRecursions(data_for_patch,
                               radius = 50, timeunits = "mins")

# assign to recurse data
data_for_patch[, res_time := recurse_stats$residenceTime]

@@

We subset data with a residence time > 5 minutes.

@@

# on known residence points
patch_res_known <- atl_res_patch(data_for_patch[res_time >= 5, ], 
                                buffer_radius = 5,
                                lim_spat_indep = 50,
                                lim_time_indep = 5,
                                min_fixes = 3)
```
